AIR4children: Artificial Intelligence and Robotics for Children

### 2021-02-03 article/tex/submission.tex
polishes introduction; adds references, air4children-v00 figure

\author{Co-author B}
\affiliation{%
\institution{University of A}
\streetaddress{Adress}
\city{City}
\country{Country}}
\email{email@internet.org}

@@

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

@@

\section{Introduction}

Current progress in the fields of Artificial Intelligence and Robotics (AIR)
is accelerating specially in countries where innonavtion and technologies are happenigs. 
However, even thought these fields are growing work is in progress in separated streams
for AI and Robotics, there is little work that put together both fields and with
little to none focus on children. With this in mind this work is proposing 
the term AIR4children in a way to offer pedagogical, open-source software and hardware
tools to balance the current posiblities for children to enjoy and to dicover these 
fields from a children-like perspective.
As pointed in the guidance of AI for children by UNICEF \cite{UNICEF2020},
there are many challenges to make inclusive AIR, in this case, 
from any or idealialy under-represented communities and provie fairness and non-discrimination 
in child-robot interaction as well as design curriculums for children of different 
socieconomical backgrounds, developmental stages or learning abilitities. 
The aim of the AIR4children is to prepare children for present 
to contribute to resposnbile AIR for the present and the future.

Anoother aspects as the socialbitly of robots are well explamplied with 
Jibo [REF], Cosmos [REF] and more recently Shelly, a tortoise-like robot, to tacke 
multiple interaction of one-to-many as well the resctrition of children
abusive behaviours towards robots \cite{hu2018}.

@@

@@

>>>>

\author{Co-author B}
\affiliation{%
\institution{University of B}
\streetaddress{Adress}
\city{City}
\country{Country}}
\email{email@internet.org}

@@

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{../figures/air4children/versions/drawing-v00.png}
  \caption{(a)open-source software and hardware, (b) non-traditional curriculums, (c) free for anyone.}
  \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

@@

\section{Introduction} 
The scientific and techonlogical progress in the fields of Artificial Intelligence and Robotics (AIR) is rapdily moving forward over the past decade. 
Advances in AIR are mainly in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
As the fielfs of AIR are advancing at a great pace, there are opportunties to for more child-centered AIR and with various challenges for children in places where resources are scarse. 
Recently, a drafted guidance of AI for children by UNICEF \cite{UNICEF2020} pointed out various challenges of making such filed avaiable to under-represented communities with the aim of providing fairness and non-discrimination.
With this in mind this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to create and to design tools based on open-sourced projects.
Similarly, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socieconomical backgrounds, developmental stages or learning abilitities. 
%Anoother aspects as the socialbitly of robots are well explamplied with 
%Jibo [REF], Cosmos [REF] and more recently Shelly, a tortoise-like robot, to tacke 
%multiple interaction of one-to-many as well the resctrition of children
%abusive behaviours towards robots \cite{hu2018}.

@@

  Deep Learning (DL) is a branch of machine learning in Artificial Intelligence
  which essentially takes advantage of a huge datasets to train neural networks.
  The great impact of DL in recent years is also because of improvements in 
  hardware development and mainly because of open source tools and libraries \cite{matelabs2017}.
  Additionally to that, there is a huge range of applications in areas such as robotics,
  transportation, medicine and last but not least in education.
  That said, we propose to use a raspberry pi, a $\pounds$30 board with
  GNU/Linux OS, connected with a mini arduino board, $\pounds$2 board,  servomotors 
  and pi camera in order to create a simple low-cost educational robot 
  where children can learn the basics concepts of robotics and deep learning \cite{durr2015}.

@@

Our primary aim for Libre Robotics is to build low-cost education robots 
which will be helpful to teach many didactic activities where children 
can interact with the robot and learn concepts of robotics, linear algebra, 
machine learning, and deep learning.
One example is the implementation of a low-cost robot with 
convolutional neural networks that recognise six basic face emotions: 
happy, sad, surprise, fear, anger and neutral \cite{ho2016, Ruiz-Garcia2016}.

%
